---
title: "Simulation Runner"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and simulation functions

```{r}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(purrr))
suppressPackageStartupMessages(library(readr))
suppressPackageStartupMessages(library(doParallel))
suppressPackageStartupMessages(library(doRNG))
suppressPackageStartupMessages(library(here))
source("simulation_core.R")
```

## Setup Simulation Options

### 1. Initial Values and Other Parameters

Here, you can specify the parameter values to search as vectors supplied to the x1, x2, ..., input2_on_at_min arguments.

Also, specify the number of cores for the parallel computation.

Suggestion: Start with a limited number of parameters in each vector before you run huge numbers of parameters. Look for the output from this cell to find how many simulations you have requested.

```{r}
initial_condition_df <- cross_initial_conditions(
  x1 = c(1),
  x2 = c(0.25, 0.5, 0.75, 1.0, 1.25, 1.5, 1.75, 2.0),
  x3 = c(1),
  x4 = c(0.25, 0.5, 0.75, 1.0, 1.25, 1.5, 1.75, 2.0),
  x5 = c(1),
  h42 = c(0.65, 0.675, 0.7, 0.725, 0.75, 0.775, 0.8, 0.825, 0.85),
  input2_off_at_min = c(30),
  input2_on_at_min = c(60)
)

print(paste("Number of simulations requested:", nrow(initial_condition_df), sep = " "))

run_specs <- create_run_specs(initial_condition_df)
```

### 2. Make a ggplot theme for the plots

```{r}
theme_set(
  theme_linedraw() +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title = element_text(size = 12, face = "bold"),
      axis.text = element_text(size = 9)
    )
)
```

### 3. Set number of cores for computation

Set this to a value appropriate for your processor.

```{r}
num_cores <- 56
# num_cores <- 3
```

## DO NOT MODIFY BELOW THIS LINE

### Create all plots in parallel

```{r}
cl <- makeCluster(num_cores, type="PSOCK")
registerDoParallel(cl)
registerDoRNG(123)

results <- foreach(i=seq_along(run_specs), .packages = c("dplyr", "tidyr", "ggplot2")) %dopar% {
  run_spec <- run_specs[[i]]
  initial_conditions_run_and_plot(
    run_name = run_spec[["run_name"]],
    x1_initial = run_spec[["ics"]][[1]],
    x2_initial = run_spec[["ics"]][[2]],
    x3_initial = run_spec[["ics"]][[3]],
    x4_initial = run_spec[["ics"]][[4]],
    x5_initial = run_spec[["ics"]][[5]],
    h42 = run_spec[["h42"]],
    input2_off_at_min = run_spec[["input2_off_at_min"]],
    input2_on_at_min = run_spec[["input2_on_at_min"]]
  )
}

registerDoSEQ()
```

### Write csvs and plots

```{r}
star_schema_dfs <- star_schema(results)

write_csv(star_schema_dfs[["run_timeseries_wide"]], here("output", "run_timeseries_wide.csv"), col_names = TRUE, na = "")
write_csv(star_schema_dfs[["run_timeseries_long"]], here("output", "run_timeseries_long.csv"), col_names = TRUE, na = "")
write_csv(star_schema_dfs[["run_metadata"]], here("output", "run_metadata.csv"), col_names = TRUE, na = "")

write_plots(results)
```
