---
title: "Simulation Runner"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and simulation functions

```{r}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(purrr))
suppressPackageStartupMessages(library(readr))
suppressPackageStartupMessages(library(parallel))
suppressPackageStartupMessages(library(here))
source("simulation_core.R")
```

## Setup Simulation Options

### 1. Initial Values and Other Parameters

Here, you can specify the parameter values to search as vectors supplied to the x1, x2, ..., input2_on_at_min arguments.

Also, specify the number of cores for the parallel computation.

Suggestion: Start with a limited number of parameters in each vector before you run huge numbers of parameters. Look for the output from this cell to find how many simulations you have requested.

```{r}
initial_condition_df <- cross_initial_conditions(
  x1 = c(1.0),
  x2 = c(1.0),
  x3 = c(1.0),
  x4 = c(1.0),
  x5 = c(1.0),
  h42 = c(0.3, 0.4, 0.5, 0.6, 0.7),
  input2_off_at_min = c(10),
  input2_on_at_min = c(20),
  gamma_1 = c(0.0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0)
)

print(paste("Number of simulations requested:", nrow(initial_condition_df), sep = " "))

run_specs <- create_run_specs(initial_condition_df)
```

### 2. Make a ggplot theme for the plots

```{r}
theme_set(
  theme_linedraw() +
    theme(
      plot.title = element_text(size = 18, face = "bold"),
      axis.title = element_text(size = 12, face = "bold"),
      axis.text = element_text(size = 9)
    )
)
```

### 3. Set number of cores for computation

Set this to a value appropriate for your processor.

```{r}
# num_cores <- 56
num_cores <- 3
```

### Create all plots in parallel

```{r}
cl <- makeCluster(num_cores, type = "PSOCK")

cluster_eval <- clusterEvalQ(cl, {
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  source("simulation_core.R")
})

cluster_set_rng <- clusterSetRNGStream(cl, iseed = 1234)

results <- clusterApply(
  cl,
  run_specs,
  function(run_spec) {
    initial_conditions_run_and_plot(
      run_name = run_spec[["run_name"]],
      x1_initial = run_spec[["ics"]][[1]],
      x2_initial = run_spec[["ics"]][[2]],
      x3_initial = run_spec[["ics"]][[3]],
      x4_initial = run_spec[["ics"]][[4]],
      x5_initial = run_spec[["ics"]][[5]],
      h42 = run_spec[["h42"]],
      input2_off_at_min = run_spec[["input2_off_at_min"]],
      input2_on_at_min = run_spec[["input2_on_at_min"]],
      gamma_1 = run_spec[["gamma_1"]]
    )
  }
)

cluster_stop <- stopCluster(cl)
```

## or create all plots serially

```{r}
# results <- lapply(
#   run_specs,
#   function(run_spec) {
#     initial_conditions_run_and_plot(
#       run_name = run_spec[["run_name"]],
#       x1_initial = run_spec[["ics"]][[1]],
#       x2_initial = run_spec[["ics"]][[2]],
#       x3_initial = run_spec[["ics"]][[3]],
#       x4_initial = run_spec[["ics"]][[4]],
#       x5_initial = run_spec[["ics"]][[5]],
#       h42 = run_spec[["h42"]],
#       input2_off_at_min = run_spec[["input2_off_at_min"]],
#       input2_on_at_min = run_spec[["input2_on_at_min"]]
#     )
#   }
# )
```

### Write csvs and plots

```{r}
star_schema_dfs <- star_schema(results)

write_csv(star_schema_dfs[["run_timeseries_wide"]], here("output", "run_timeseries_wide.csv"), col_names = TRUE, na = "")
write_csv(star_schema_dfs[["run_timeseries_long"]], here("output", "run_timeseries_long.csv"), col_names = TRUE, na = "")
write_csv(star_schema_dfs[["run_metadata"]], here("output", "run_metadata.csv"), col_names = TRUE, na = "")

write_plots(results)
```
